Hyperparameter Learning \\ for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds

### 2018-04-02 ECML2018/paper/mce_ecml2018.tex
Convert paper and appendix to ECML format

\documentclass[twoside]{article}
\usepackage{aistats2018}
% If your paper is accepted, change the options for the package
% aistats2018 as follows:
%
%\usepackage[accepted]{aistats2018}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

\usepackage{glossaries}
\usepackage{acronym}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[colorlinks=true,linkcolor=black,citecolor=black]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

% My Packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathbbol}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{vector}
\usepackage{cleveref}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algorithmic}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}

@@

\begin{document}

	\twocolumn[

	\aistatstitle{Hyperparameter Learning for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds}

	\aistatsauthor{ Anonymous Author 1 \And Anonymous Author 2 \And Anonymous Author 3 }

	\aistatsaddress{ Unknown Institution 1 \And Unknown Institution 2 \And Unknown Institution 3 } ]

@@

		% The goal is to motivate the problem here and outline our contribution
		Conditional mean embeddings are nonparametric models that encode conditional expectations in a reproducing kernel Hilbert space, creating a flexible and powerful framework for probabilistic inference. Their performance is greatly dependent on the choice of kernel hyperparameters and regularization parameter. However, current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics. For conditional mean embeddings with categorical targets and arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing data fit against model complexity. The approach only requires batch updates, allowing scalable kernel learning without kernel approximations. Experiments demonstrate that our framework outperforms competing methods, and can be further extended to incorporate and learn neural network weights improving generalization.

		% % % Original:
		%	We propose learning-theoretic bounds for hyperparameter learning of conditional kernel embeddings for estimating multiclass probabilities. Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS). We consider an estimator for multiclass probabilities based on the conditional embedding, with proven stochastic convergence. We then prove that its expected classification error can be bounded with high probability using Rademacher complexity bounds. We use this bound to propose a scalable hyperparameter learning algorithm for conditional embeddings with batch stochastic gradient descent. We apply our learning algorithm to standard UCI datasets, as well as to learn feature representations of a convolutional neural network with improved accuracy, demonstrating the generality of this approach.
	\end{abstract}

@@

		\Glspl{CME} are attractive because they encode conditional expectations in a \gls{RKHS}, bypassing the need for a parametrized distribution \citep{song2013kernel}. They are part of a broader class of models known as kernel embeddings, where nonparametric probabilistic inference can be carried out entirely within the \gls{RKHS} because difficult marginalization integrals become simple linear algebra \citep{muandet2016kernel}. This very general framework is core to modern kernel probabilistic methods, including kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, density estimation \citep{song2008tailoring, kanagawa2014recovering}, component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery \citep{jitkrittum2016interpretable}, and state space filtering \citep{kanagawa2016filtering}.

@@

		Nevertheless, like most kernel based models, their performance is highly dependent on the hyperparameters chosen. For these models, the model selection process usually begins by selecting a kernel, whose parameters become part of the model hyperparameters, which may further include noise or regularization parameters. Given a set of hyperparameters, training is performed by solving either a convex optimization problem, such as for \glspl{SVM} \citep{scholkopf2002learning}, or a set of linear equations, such as for \gls{GPs} \citep{rasmussen2006gaussian}, \glspl{RLSC} \citep{rifkin2003regularized}, and \glspl{CME}. Unfortunately, hyperparameter tuning is not straight forward, and often cross validation \citep{song2013kernel} or median length heuristics \citep{muandet2016kernel} remain as the primary approaches for this task.

@@

		One notable success story in this domain are \gls{GPs}, which utilizes the marginal likelihood for hyperparameter learning. The marginal likelihood arises from its Bayesian formulation, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity. On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalizing the model beyond known examples.

@@

		Can we formulate a learning objective for \glspl{CME} to balance data fit and model complexity, similar to the marginal likelihood of \gls{GPs}? For \glspl{CME} with categorical targets and arbitrary input, we present such a learning objective as our main contribution. In particular, we: (1) derive a measure $r(\theta, \lambda)$ to measure the model complexity of a \gls{CME} based on the Rademacher complexity of a relevant class of \glspl{CME}, (2) propose a novel learning objective based on this complexity measure to control generalization risk by balancing data fit against model complexity, and (3) propose a scalable hyperparameter learning algorithm under this objective using batch updates. We show that this learning objective produces \glspl{CME} that generalize better than that learned from cross validation, \gls{ERM}, or median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights improving generalization accuracy. % Finally, we also discuss some variations to the \gls{MCE} model.

@@

			Hyperparameter learning for \glspl{CME} is particularly difficult compared to marginal or joint embeddings, since the kernel $k = k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularization parameter $\lambda \in \Lambda = \mathbb{R}_{+}$. \cite{lever2012conditional} proposed to hold out a validation set $\{k(x_{t_{j}}, \cdot), l(y_{t_{j}}, \cdot)\}_{j = 1}^{J}$ and minimize $\frac{1}{J} \sum_{j = 1}^{J} \big\| l(y_{t_{j}}, \cdot) - \hat{\mathcal{U}}_{Y | X} k(x_{t_{j}}, \cdot) \big\|_{\mathcal{H}_{l}}^{2}$ where $\hat{\mathcal{U}}_{Y | X}$ is estimated from the remaining training set using \eqref{eq:empirical_conditional_embedding}. This could also be repeated over multiple folds for cross validation. \cite{song2013kernel} also uses this cross validation approach, but adds a regularization $\lambda \| \mathcal{U} \|^{2}_{HS}$ to the validation objective. This approach improves generalization of \glspl{CME} to unseen examples. However, they require the selection for the split and number of folds. Moreover, they are not optimized for any particular prediction task. By fitting a separate model for each fold during learning, they also incur a large computational cost of $O(J n^{3})$ for $J$ folds, and becomes prohibitive with large datasets.

@@

		Let $p_{c}(x) := \mathbb{P}[Y = c | X = x]$ be the \textit{decision probability function} for class $c \in \mathbb{N}_{m}$, which is the probability of the class label $Y$ being $c$ when the example $X$ is $x$. Note that there are no restrictions on the input domain $\mathcal{X}$ as long as a kernel $k$ can be defined on it. For example, $x$ could be a continuous variable in $\mathcal{X} = \mathbb{R}^{d}$. We begin by writing this probability as an expectation of indicator functions,
		\begin{equation}
		p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
		\label{eq:decision_probability}
		\end{equation}	
		With $\mathbb{1}_{c} \in \mathcal{H}_{\delta}$, we let $g = \mathbb{1}_{c}$ in \eqref{eq:empirical_conditional_expectation} and $\bvec{1}_{c} := \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n}$ to estimate the right hand side of \eqref{eq:decision_probability} by
		\begin{equation}
		\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
		\label{eq:empirical_decision_probability}
		\end{equation}
		Let $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ be the one hot encoded labels of $\{y_{i}\}_{i = 1}^{n}$. The vector of empirical decision probabilities over the classes $c \in \mathbb{N}_{m}$ is then
		\begin{equation}
		\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) \in \mathbb{R}^{m}.
		\label{eq:empirical_decision_probability_vector}
		\end{equation}
		Since $\mathcal{U} = \hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the solution to a regularized least squares problem in the RKHS from $k(x, \cdot) \in \mathcal{H}_{k}$ to $l(y, \cdot) \in \mathcal{H}_{l}$ \citep{lever2012conditional}, \glspl{CME} can be seen as \glspl{KRR} in the \gls{RKHS}. In this case, because $\mathcal{Y} = \mathbb{N}_{m}$ is discrete, $\mathcal{H}_{\delta}$ can be identified with $\mathbb{R}^{m}$. As a result, for discrete $\mathcal{Y} = \mathbb{N}_{m}$ the rows of the \gls{MCE} can also be seen as $m$ \glspl{KRR} \citep{friedman2001elements} on binary $\{0, 1\}$-targets, where they all share the same input kernel. We now verify that the empirical decision probabilities \eqref{eq:empirical_decision_probability} do converge to the population decision probability.

@@

		In particular, the assumption $k(x, \cdot) \in \mathrm{image}(C_{XX})$ is on the input kernel $k$, not the output kernel $l$, which is a Kronecker delta $l = \delta$ for \glspl{MCE}. In practice, this assumption can be relaxed through introducing the regularization parameter $\lambda$ as in \eqref{eq:empirical_conditional_embedding} \citep{song2009hilbert}.

@@

		We begin by defining a loss function as a measure for performance. For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ whose entries are probability estimates, we employ a modified cross entropy loss,
		\begin{equation}
		\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
		\label{eq:cross_entropy_loss_copy}
		\end{equation}
		to express risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$ where usually $\epsilon << 1$. Note that we employ the loss on the original probability estimates \eqref{eq:empirical_decision_probability_vector}, not the clip-normalized version \eqref{eq:empirical_decision_probability_clip_normalized}. We employ this loss in virtue of \cref{thm:probability_convergence_copy}, where we expect $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector} to be close to the population decision probability. In contrast, direct outputs from \glspl{SVC}, \glspl{GPC}, or \glspl{RLSC} are not consistent probability estimates and cannot take advantage of \eqref{eq:cross_entropy_loss_copy} easily.

@@

			\begin{equation}
			\begin{aligned}
				&\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))]  \\
				&\leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \; \alpha \rho + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}}.
			\end{aligned}
			\label{eq:specific_expected_loss_bound_for_multiclass_conditional_embedding_copy}
			\end{equation}

@@

			For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$ used to define $\bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector}, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta$, $\lambda \in \Lambda$, and $\epsilon \in (0, e^{-1})$ satisfies
			\begin{equation}
			\begin{aligned}
			&\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \\
			&\leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \; r(\theta, \lambda) + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}},
			\label{eq:expected_risk_bound_hyperparameter_learning_copy}
			\end{aligned}
			\end{equation}
			where $r(\theta, \lambda) := \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda}) \sup_{x \in \mathcal{X}} k_{\theta}(x, x)}$ and $V_{\theta, \lambda} := (K_{\theta} + n \lambda I)^{-1} \bvec{Y}$.
			See Theorem B.8 of Appendix B for proof.
		\end{theorem}

@@

	\newpage
	\bibliography{kernel_embedding}
	\bibliographystyle{apalike}

>>>>

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration

@@

% Default packages
\usepackage{glossaries}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[colorlinks=true,linkcolor=black,citecolor=black]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

% My Packages
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{amsthm}
\usepackage{mathbbol}
\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{vector}
\usepackage{cleveref}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{claim}[theorem]{Claim}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algorithmic}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}

@@

%
\title{Hyperparameter Learning \\ for Conditional Mean Embeddings \\ with Rademacher Complexity Bounds}

\titlerunning{Hyperparameter Learning for Conditional Mean Embeddings}
% abbreviated title (for running head), also used for the TOC unless \toctitle is used

\author{Kelvin Hsu \inst{1, 2} \and
		Richard Nock \inst{1, 2, 3} \and
		Fabio Ramos \inst{1, 2}}
%
\authorrunning{Hsu et. al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Kelvin Hsu, Richard Nock, Fabio Ramos}
%
\institute{	University of Sydney, Sydney, Australia, \\ \and
			Data61, CSIRO, Sydney, Australia \\ \and
			Australian National University, Canberra, Australia}

\begin{document}
	%
	\frontmatter          % for the preliminaries
	\maketitle            % typeset the title of the contribution
	%

@@

		% The goal is to motivate the problem here and outline our contribution
		Conditional mean embeddings are nonparametric models that encode conditional expectations in a reproducing kernel Hilbert space, creating a flexible and powerful framework for probabilistic inference. Their performance is greatly dependent on the choice of kernel hyperparameters and regularization parameter. However, current approaches for hyperparameter tuning predominantly rely on cross validation and distance based heuristics. For conditional mean embeddings with categorical targets and arbitrary inputs, we propose a hyperparameter learning framework based on Rademacher complexity bounds to prevent overfitting by balancing data fit against model complexity. The approach only requires batch updates, allowing scalable kernel hyperparameter tuning without kernel approximations. Experiments demonstrate that our framework outperforms competing methods, and can be further extended to incorporate and learn neural network weights improving generalization.

		\keywords{Conditional Mean Embeddings, Kernel Mean Embeddings, Kernel Methods, Mean Embeddings, Hilbert Space Embeddings, Hyperparameter Learning, Rademacher Complexity}
		% % % Original:
		%	We propose learning-theoretic bounds for hyperparameter learning of conditional kernel embeddings for estimating multiclass probabilities. Kernel embeddings are nonparametric methods to represent probability distributions directly through observed data in a reproducing kernel Hilbert space (RKHS). We consider an estimator for multiclass probabilities based on the conditional embedding, with proven stochastic convergence. We then prove that its expected classification error can be bounded with high probability using Rademacher complexity bounds. We use this bound to propose a scalable hyperparameter learning algorithm for conditional embeddings with batch stochastic gradient descent. We apply our learning algorithm to standard UCI datasets, as well as to learn feature representations of a convolutional neural network with improved accuracy, demonstrating the generality of this approach.
	\end{abstract}

@@

	\Glspl{CME} are attractive because they encode conditional expectations in a \gls{RKHS}, bypassing the need for a parametrized distribution \citep{song2013kernel}. They are part of a broader class of techniques known as kernel mean embeddings, where nonparametric probabilistic inference can be carried out entirely within the \gls{RKHS} because difficult marginalization integrals become simple linear algebra \citep{muandet2016kernel}. This very general framework is core to modern kernel probabilistic methods, including kernel two-sample testing \citep{gretton2007kernel}, kernel Bayesian inference  \citep{fukumizu2013kernel}, density estimation \citep{song2008tailoring, kanagawa2014recovering}, component analysis \citep{muandet2013domain}, dimensionality reduction \citep{fukumizu2004dimensionality}, feature discovery \citep{jitkrittum2016interpretable}, and state space filtering \citep{kanagawa2016filtering}.

@@

	Nevertheless, like most kernel based models, their performance is highly dependent on the hyperparameters chosen. For these models, the model selection process usually begins by selecting a kernel, whose parameters become part of the model \textit{hyperparameters}, which may further include noise or regularization parameters. Given a set of hyperparameters, training is performed by solving either a convex optimization problem, such as for \glspl{SVM} \citep{scholkopf2002learning}, or a set of linear equations, such as for \gls{GPs} \citep{rasmussen2006gaussian}, \glspl{RLSC} \citep{rifkin2003regularized}, and \glspl{CME}. Unfortunately, hyperparameter tuning is not straight forward, and often cross validation \citep{song2013kernel} or median length heuristics \citep{muandet2016kernel} remain as the primary approaches for this task. The former can be expensive and sensitive to the selection and number of validation sets, while the latter heuristic only applies to hyperparameters with a length scale interpretation and makes no reference to the conditional inference problem involved.

@@

	One notable success story in this domain are \gls{GPs}, which utilizes the marginal likelihood objective for hyperparameter learning. The marginal likelihood arises from its Bayesian formulation, and exhibits certain desirable properties -- in particular, the ability to automatically balance between data fit and model complexity. On the other hand, \glspl{CME} are not necessarily Bayesian, and hence they do not benefit from a natural marginal likelihood formulation, yet such a balance is critical when generalizing the model beyond known examples.

@@

	Can we formulate a learning objective for \glspl{CME} to balance data fit and model complexity, similar to the marginal likelihood of \gls{GPs}? For \glspl{CME} with categorical targets and arbitrary input, we present such a learning objective as our main contribution. In particular, we: (1) derive a measure $r(\theta, \lambda)$ to measure the model complexity of a particular \gls{CME} based on the Rademacher complexity of a class of \glspl{CME} determined by that particular \gls{CME}, (2) propose a novel learning objective based on this complexity measure to control generalization risk by balancing data fit against model complexity, and (3) propose a scalable hyperparameter learning algorithm under this objective using batch updates. We show that this learning objective produces \glspl{CME} that generalize better than that learned from cross validation, \gls{ERM}, or median length heuristics on standard benchmarks, and apply such an algorithm to incorporate and learn neural network weights improving generalization accuracy. % Finally, we also discuss some variations to the \gls{MCE} model.

@@

	Hyperparameter learning for \glspl{CME} is particularly difficult compared to marginal or joint embeddings, since the kernel $k = k_{\theta}$ with parameters $\theta \in \Theta$ is to be learned jointly with a regularization parameter $\lambda \in \Lambda = \mathbb{R}_{+}$. \cite{lever2012conditional} proposed to hold out a validation set $\{k(x_{t_{j}}, \cdot), l(y_{t_{j}}, \cdot)\}_{j = 1}^{J}$ and minimize $\frac{1}{J} \sum_{j = 1}^{J} \big\| l(y_{t_{j}}, \cdot) - \hat{\mathcal{U}}_{Y | X} k(x_{t_{j}}, \cdot) \big\|_{\mathcal{H}_{l}}^{2}$ where $\hat{\mathcal{U}}_{Y | X}$ is estimated from the remaining training set using \eqref{eq:empirical_conditional_embedding}. This could also be repeated over multiple folds for cross validation. \cite[p. 15]{song2013kernel} also uses this cross validation approach, but adds a regularization $\lambda \| \mathcal{U} \|^{2}_{HS}$ to the validation objective. Validation sets are necessary for improving generalization to unseen examples as the \gls{CME} is already the solution that minimizes the objective from \cite{lever2012conditional} over the operator space, so further optimization over the hyperparmeters using the same training set would lead to overfitting. Moreoever, they require the selection for the split and number of folds, and are not optimized for any particular inference task. By fitting a separate model for each fold during learning, they also incur a large computational cost of $O(J n^{3})$ for $J$ folds, and becomes prohibitive with large datasets. This spells a need for an alternative hyperparameter learning framework using a different objective.

@@

	Let $p_{c}(x) := \mathbb{P}[Y = c | X = x]$ be the \textit{decision probability function} for class $c \in \mathbb{N}_{m}$, which is the probability of the class label $Y$ being $c$ when the example $X$ is $x$. Note that there are no restrictions on the input domain $\mathcal{X}$ as long as a kernel $k$ can be defined on it. For example, $x$ could be a continuous variable in $\mathcal{X} = \mathbb{R}^{d}$. We begin by writing this probability as an expectation of indicator functions,
	\begin{equation}
	p_{c}(x) := \mathbb{P}[Y = c | X = x] = \mathbb{E}[\mathbb{1}_{c}(Y) | X = x].
	\label{eq:decision_probability}
	\end{equation}	
	With $\mathbb{1}_{c} \in \mathcal{H}_{\delta}$, we let $g = \mathbb{1}_{c}$ in \eqref{eq:empirical_conditional_expectation} and $\bvec{1}_{c} := \{\mathbb{1}_{c}(y_{i})\}_{i = 1}^{n}$ to estimate the right hand side of \eqref{eq:decision_probability} by
	\begin{equation}
	\hat{p}_{c}(x) = f_{c}(x) := \bvec{1}_{c}^{T} (K + n \lambda I)^{-1} \bvec{k}(x).
	\label{eq:empirical_decision_probability}
	\end{equation}
	Let $\bvec{Y} := \begin{bmatrix} \bvec{1}_{1} & \bvec{1}_{2} & \cdots & \bvec{1}_{m} \end{bmatrix} \in \{0, 1\}^{n \times m}$ be the one hot encoded labels of $\{y_{i}\}_{i = 1}^{n}$. The vector of empirical decision probabilities over the classes $c \in \mathbb{N}_{m}$ is then
	\begin{equation}
	\hat{\bvec{p}}(x) = \bvec{f}(x) := \bvec{Y}^{T} (K + n \lambda I)^{-1} \bvec{k}(x) \in \mathbb{R}^{m}.
	\label{eq:empirical_decision_probability_vector}
	\end{equation}
	Since $\mathcal{U} = \hat{\mathcal{U}}_{Y | X}$ \eqref{eq:empirical_conditional_embedding} is the solution to a regularized least squares problem in the RKHS from $k(x, \cdot) \in \mathcal{H}_{k}$ to $l(y, \cdot) \in \mathcal{H}_{l}$ \citep{lever2012conditional}, \glspl{CME} are essentially \glspl{KRR} in the \gls{RKHS}. In this case, because $\mathcal{Y} = \mathbb{N}_{m}$ is discrete, $\mathcal{H}_{\delta}$ can be identified with $\mathbb{R}^{m}$. As a result, for discrete $\mathcal{Y} = \mathbb{N}_{m}$ the rows of the \gls{MCE} can also be seen as $m$ \glspl{KRR} \citep{friedman2001elements} on binary $\{0, 1\}$-targets, where they all share the same input kernel. Because they all share the same kernel to form the \gls{MCE}, we can leverage this fact and show that the empirical decision probabilities \eqref{eq:empirical_decision_probability} do converge to the population decision probability.

@@

	In particular, the assumption $k(x, \cdot) \in \mathrm{image}(C_{XX})$ is on the input kernel $k$, not the output kernel $l$, which is a Kronecker delta $l = \delta$ for \glspl{MCE}. It is worthwhile to note that this assumption is common for \glspl{CME}, and is not as restrictive as it may first appear, as it can be relaxed through introducing the regularization parameter $\lambda$ \eqref{eq:empirical_conditional_embedding} in practice \citep[p.74-75, Sec. 3 and 3.1 \textit{resp.}]{song2009hilbert, song2013kernel, muandet2016kernel}.

@@

	We begin by defining a loss function as a measure for performance. For decision functions of the form $\bvec{f} : \mathcal{X} \to \mathcal{A} = \mathbb{R}^{m}$ whose entries are probability estimates, we employ a modified cross entropy loss,
	\begin{equation}
	\mathcal{L}_{\epsilon}(y, \bvec{f}(x)) := - \log{ [\bvec{y}^{T} \bvec{f}(x)]_{\epsilon}^{1} } = - \log{ [f_{y}(x)]_{\epsilon}^{1} },
	\label{eq:cross_entropy_loss_copy}
	\end{equation}
	to express risk, where we use the notation $[\;\cdot\;]_{\epsilon}^{1} := \min\{\max\{\;\cdot\;, \epsilon\}, 1\}$ for $\epsilon \in (0, 1)$ where usually $\epsilon << 1$. It is worthwhile to point out that this choice only makes sense due to \cref{thm:probability_convergence_copy}, as it allows us to interpret the outputs of the \gls{CME} as asymptotic probability estimates. Note that we employ the loss on the original probability estimates \eqref{eq:empirical_decision_probability_vector}, not the clip-normalized version \eqref{eq:empirical_decision_probability_clip_normalized}. We employ this loss in virtue of \cref{thm:probability_convergence_copy}, where we expect $\bvec{f}(x)$ \eqref{eq:empirical_decision_probability_vector} to be close to the population decision probability. In contrast, direct outputs from \glspl{SVC}, \glspl{GPC}, or \glspl{RLSC} are not consistent probability estimates and cannot take advantage of \eqref{eq:cross_entropy_loss_copy} easily.

@@

		\begin{equation}
		\begin{aligned}
		\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, f(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, f(X_{i})) + 4 e \; \alpha \rho + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}}.
		\end{aligned}
		\label{eq:specific_expected_loss_bound_for_multiclass_conditional_embedding_copy}
		\end{equation}

@@

		For any integer $n \in \mathbb{N}_{+}$ and any set of training observations $\{x_{i}, y_{i}\}_{i = 1}^{n}$ used to define $\bvec{f}_{\theta, \lambda}$ \eqref{eq:empirical_decision_probability_vector}, with probability $1 - \beta$ over \textit{iid} samples $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of length $n$ from $\mathbb{P}_{X Y}$, every $\theta \in \Theta$, $\lambda \in \Lambda$, and $\epsilon \in (0, e^{-1})$ satisfies
		\begin{equation}
		\begin{aligned}
		\mathbb{E}[\mathcal{L}_{e^{-1}}(Y, \bvec{f}_{\theta, \lambda}(X))] \leq \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(Y_{i}, \bvec{f}_{\theta, \lambda}(X_{i})) + 4 e \; r(\theta, \lambda) + \sqrt{\frac{8}{n} \log{\frac{2}{\beta}}},
		\label{eq:expected_risk_bound_hyperparameter_learning_copy}
		\end{aligned}
		\end{equation}
		where $r(\theta, \lambda) := \sqrt{\mathrm{trace}(V_{\theta, \lambda}^{T} K_{\theta} V_{\theta, \lambda}) \sup_{x \in \mathcal{X}} k_{\theta}(x, x)}$ and $V_{\theta, \lambda} := (K_{\theta} + n \lambda I)^{-1} \bvec{Y}$.
		See Theorem B.8 of Appendix B for proof.
	\end{theorem}

@@

%	\begin{thebibliography}{}
	\small{
	\bibliography{kernel_embedding}
	\bibliographystyle{apalike}
	}
%	\end{thebibliography}
